---
title: "Convert preprocess lambda function"
output: html_notebook
---

__Objective__
Reproduce the `preprocess` lambda function.

**Recipe**
1. Build the preprocess function using an anonymous function
2. Build the function `get_moments` which will be part of the anonymous function
3. Test `preprocess` in R and compare to Python results

**Challenges**
- The PyTorch function `reshape` in R receives parameters in different way than Python. In Python it is `mean.reshape(1,)`, while in R is `torch$reshape(mean, list(1L))`
- The PyTorch function `cat` works like this `torch.cat((t1, t2, t3, t4))`, while in R we have to use `torch$cat(c(t1, t2, t3, t4))` to concatenate the tensors.

## R version

```{r}
library(rTorch)


torch$manual_seed(123L)
np$random$seed(seed=123L)

# Data params
data_mean = 4
data_stddev = 1.25


# lambda functions
name         <- "Only 4 moments"
preprocess   <- function(data) get_moments(data)
d_input_func <- function(x) 4


get_distribution_sampler <- function(mu, sigma) {
    # torch.Tensor(np.random.normal(mu, sigma, (1, n)))
    # the last member of the normal is the shape vector
    function(n) torch$Tensor(np$random$normal(mu, sigma, c(1L, n)))
}

get_generator_input_sampler <- function(){
    # lambda m, n: torch.rand(m, n) 
    function(m, n) torch$rand(m, n)
}

d_sampler <- get_distribution_sampler(data_mean, data_stddev)

get_moments <- function(d) {
    mean <- torch$mean(d)
    diffs <- d - mean
    var <- torch$mean(torch$pow(diffs, 2.0))
    std <- torch$pow(var, 0.5)
    zscores <- diffs / std
    skews <- torch$mean(torch$pow(zscores, 3.0))
    kurtoses <- torch$mean(torch$pow(zscores, 4.0)) - 3.0
    # torch.cat((mean.reshape(1,), std.reshape(1,), skews.reshape(1,), kurtoses.reshape(1,)))
    final <- torch$cat(c(torch$reshape(mean, list(1L)), torch$reshape(std, list(1L)),
                       torch$reshape(skews, list(1L)), torch$reshape(kurtoses, list(1L))))
    return(final)    
}

d_input_size = 500L
d_real_data = d_sampler(d_input_size)
preprocess(d_real_data)
```


## Python version

```{python}
# Generative Adversarial Networks (GAN) example in PyTorch. Tested with PyTorch 0.4.1, Python 3.6.7 (Nov 2018)
# See related blog post at https://medium.com/@devnag/generative-adversarial-networks-gans-in-50-lines-of-code-pytorch-e81b79659e3f#.sch4xgsa9

import numpy as np
import time
import torch
import torch.nn as nn
import torch.optim as optim
from torch.autograd import Variable


torch.manual_seed(123)
np.random.seed(seed=123)

# Data params
data_mean = 4
data_stddev = 1.25

# ### Uncomment only one of these to define what data is actually sent to the Discriminator
# (name, preprocess, d_input_func) = ("Raw data", lambda data: data, lambda x: x)
# (name, preprocess, d_input_func) = ("Data and variances", lambda data: decorate_with_diffs(data, 2.0), lambda x: x * 2)
# (name, preprocess, d_input_func) = ("Data and diffs", lambda data: decorate_with_diffs(data, 1.0), lambda x: x * 2)
(name, preprocess, d_input_func) = ("Only 4 moments", lambda data: get_moments(data), lambda x: 4)

print("Using data [%s]" % (name))

# ##### DATA: Target data and generator input data


def get_distribution_sampler(mu, sigma):
    # Bell curve
    return lambda n: torch.Tensor(np.random.normal(mu, sigma, (1, n)))  # Gaussian


def get_generator_input_sampler():
    return lambda m, n: torch.rand(m, n)   # Uniform-dist data into generator, _NOT_ Gaussian


def get_moments(d):
    # Return the first 4 moments of the data provided
    mean = torch.mean(d)
    diffs = d - mean
    var = torch.mean(torch.pow(diffs, 2.0))
    std = torch.pow(var, 0.5)
    zscores = diffs / std
    skews = torch.mean(torch.pow(zscores, 3.0))
    kurtoses = torch.mean(torch.pow(zscores, 4.0)) - 3.0  # excess kurtosis, should be 0 for Gaussian
    print(mean)
    print(mean.reshape(1,))
    print(std)
    final = torch.cat((mean.reshape(1,), std.reshape(1,), skews.reshape(1,), kurtoses.reshape(1,)))
    return final
```

```{python}
d_sampler = get_distribution_sampler(data_mean, data_stddev)

d_input_size = 500
d_real_data = d_sampler(d_input_size)
preprocess(d_real_data)
```



## sandbox

### `torch.reshape`

```{python}
a = torch.arange(4.)
torch.reshape(a, (2, 2))
```

```{r}
a = torch$arange(4.)
torch$reshape(a, c(2L, 2L))
```

```{r}
# concatenating tensors with cat()
# use cat(c(t1, t2))
x <- torch$tensor(3.9517)
y <- torch$tensor(1.2540)
x$reshape(1L)
y$reshape(1L)
torch$cat(c(x$reshape(1L), y$reshape(1L)))
```

