---
title: "Generate samples using Python code (no plot)"
output: html_notebook
---

## Generating multiple samples

```{r}
library(rTorch)
library(tictoc)

tic()
# gan_noplot.py lives under notebooks/ folder
# gan <- reticulate::import("gan_noplot")   # import Python script
gan   <- import("gan_noplot")   # import available in rTorch
train <- gan$train
sample <- vector("list")
for (i in seq(1:10)) {
    cat("sample:", i, "\n")
    ret_values = train()
    cat(sprintf("mean: %f; sd: %f\n", mean(ret_values), sd(ret_values)))
    print(fivenum(ret_values))
    sample[[i]] <- ret_values     # save samples in a list vector
}
toc()
```

```
seed   epochs  samples   fivenum                                           elapsed  from
123     500      10      4.683814  6.960758 10.527839 10.842631 10.882711    151.4  Rmarkdown
123     500      10      4.683814  6.960758 10.527839 10.842631 10.882711    168.5  Rmarkdown
123    5000      10      1.043203 3.473358 3.916274 4.637702 6.908193       1402.5  Rmarkdown
123    5000      10      1.043203 3.473358 3.916274 4.637702 6.908193       1365.5  Rmarkdown
123    2500      10      0.9962399 3.3405763 3.9121076 4.4953659 6.7830439   808.7  Rmarkdown 
123    5000      10      1.043203 3.473358 3.916274 4.637702 6.908193       1674.1  Rmarkdown
123    2500      10      0.9962399 3.3405763 3.9121076 4.4953659 6.7830439   832.8  Rmarkdown
123    1350      10      2.967617 4.598238 5.950178 6.130955 6.161784        421.3  Rmarkdown
123    1350      10      2.967617 4.598238 5.950178 6.130955 6.161784        379.5  Rmarkdown
123     500      10      4.683814  6.960758 10.527839 10.842631 10.882711    133.3  Rmarkdown
123     500      10      4.683814  6.960758 10.527839 10.842631 10.882711    136.5  Rmarkdown
123     500      10      3.061919 3.302748 3.547017 4.564566 7.119848        144.2  Rmarkdown
```

```{r}
lapply(sample, hist)
save(sample, file = "s123e5000_2.rda")
```

```{r}
lapply(sample, hist, breaks=60)
# lapply(sample, function(x) hist(x, breaks=60))
```


> Observations
1. The more epochs are added, the more normal the distribution will look.
2. There are some distributions that are skewed to the right or the left but are one or two from the ten samples.
3. The distribution samples can be reproduced by applying seeds to numpy and PyTorch.
4. To be able to make the seeds and sampling repeatable it is critical to restart the run environment so it is all started from scratch.
5. The speed at running the train() function from R is the same as running the same train() function from Python itself.



```{r}
library(rTorch)
```



```{python}
# Generate only one sample from training. No external loop.
import time
t = time.time()

from gan_noplot import train  # this script is under notebooks. same folder.

for i in range(10):
    ret_values = train()
    print(ret_values)

elapsed = time.time() - t
print("Elapsed time (s)\n", elapsed)
```

```{python}
from py_functions import fivenum
fivenum(ret_values)
```


```
seed epochs samples   fivenum                                                     elapsed
123  5000   10       [1.04320347, 3.47335768, 3.91627431, 4.63770247, 6.90819263]  1554s

```
