---
title: "Load saved synthetic datasets"
output: html_notebook
---

**Objective**
Load a saved .Rdata file to start producing plots. We don't perform any iterations here.

**Recipe**
1. Load a .Rdata file with metrics and synthetic data
2. Convert the metrics and synthetic data objects from lists to dataframes
3. Plot mean and SD for each of the ten samples
4. Plot histograms for each of the sythetic datasets
5. Boxplots comparing each of the synthetics datasets
6. Boxplots comparing the real data to the synthetic datasets


```{r}
load(file = "metrics_s123e5000-2.rda")
```

```{r}
# extract key values from the list and return as dataframe
get_epoch <- function(x) {
    data.frame(run = x$i, epoch = x$epoch, synth_mean = x$mean_fake, synth_sd = x$sd_fake)
}

# mean and standard deviation table
mean_sd_10  <- lapply(metrics, get_epoch)
all_mean_sd <- do.call(rbind, mean_sd_10)
all_mean_sd
```


```{r}
# dataframe for all the sythetic datasets
synth_data_df <- do.call(rbind, synth_data)
synth_data_df
```


```{r fig.height=4.5, fig.width=9}
# histogram with ggplot2
library(dplyr)
library(ggplot2)


ggplot(all_mean_sd, aes(x = epoch, y = synth_mean)) +
    geom_point(alpha = 0.3, size = 0.01, color = "darkgreen") +
    geom_hline(aes(yintercept = 4), linetype = "dotted") + 
    scale_y_continuous(name="Mean", breaks = c(0, 2, 4, 6, 8, 10, 12)) +
    scale_x_continuous(name="epoch", limits = c(0, 6000)) +
    facet_wrap(. ~ run, nrow = 2) +
    labs(title = "Mean")
```

```{r fig.height=4.5, fig.width=9}
# histogram with ggplot2
library(dplyr)
library(ggplot2)


ggplot(all_mean_sd, aes(x = epoch, y = synth_sd)) +
    geom_point(alpha = 0.3, size = 0.01, color = "blue") +
    geom_hline(aes(yintercept = 1), linetype = "dotted") + 
    scale_y_continuous(name="SD", breaks = c(0, 1, 2, 3, 4, 5)) +
    scale_x_continuous(name="epoch", limits = c(0, 6000)) +
    facet_wrap(. ~ run, nrow = 2) +
    labs(title = "Standard Deviation")
```

```{r}
# run the mean and standard deviation on the synthetic data samples
library(dplyr)

synth_data_df %>% 
    group_by(run) %>% 
    summarise(mean(data), sd(data))

```

```{r}
# facets for all synthetic datasets
ggplot(synth_data_df, aes(x = data)) +
    geom_histogram(bins = 50) +
    facet_wrap(. ~ run, nrow=2)
```

## Boxplots

```{r}
ggplot(synth_data_df, aes(x = run, y = data, group = run)) +
    geom_boxplot() +
    scale_x_discrete(name = "Sample #", limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10))
    
```


```{r}
ggplot(synth_data_df, aes(x = run, y = data, group = run)) +
    geom_boxplot() +
    geom_jitter(shape=16, position=position_jitter(0.2), alpha = 0.25) + 
    scale_x_discrete(name = "Sample #", limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10 ))
    
```


```{r fig.width=9}
ggplot(synth_data_df, aes(x = run, y = data, group = run)) +
    geom_violin(trim = FALSE) +
    stat_summary(fun.y=mean, geom="point", shape=23, size=2) +
    stat_summary(fun.y=median, geom="point", size=2, color="red") +
    scale_x_discrete(name = "Sample #", limits = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10 ))
```


```{r}
# load the real data
library(dplyr)

real_data <- read.csv(file = "s123-real_data.csv")
real_data

# add run number and rename column
real_data_df <- 
real_data %>% 
    mutate(run = 0, data = x, class = "real") %>% 
    select(run, data, class) %>% 
    print
    
```

```{r}
# add column to indicate it is synthetic data
synth_data_df$class <- "synth"

# combine real and synthetic data
real_plus_synth <- rbind(synth_data_df, real_data_df)
real_plus_synth
```

```{r}
# plot real and synthetic data
ggplot(real_plus_synth, aes(x = run, y = data, group = run, color = class)) +
    geom_boxplot() +
    geom_jitter(shape = 10, position = position_jitter(0.2), alpha = 0.20) +
    scale_x_discrete(name = "Sample #", limits = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10))
    
```


```{r}
library(dplyr)
# load the real data
real_data <- read.csv(file = "s123-real_data.csv")
real_data
# add run number 0 for the rel dataset and rename column
real_data_df <- 
real_data %>% 
    mutate(run = 0, data = x, class = "real") %>% 
    select(run, data, class) %>% 
    print
# add column to indicate it is synthetic data
synth_data_df$class <- "synth"
# combine real and synthetic data
real_plus_synth <- rbind(synth_data_df, real_data_df)
real_plus_synth
# plot real and synthetic data
ggplot(real_plus_synth, aes(x = run, y = data, group = run, color = class)) +
    geom_boxplot() +
    geom_jitter(shape = 10, position = position_jitter(0.2), alpha = 0.20) +
    scale_x_discrete(name = "Sample #", limits = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10))
```

