---
title: "Retrieve synthetic data and GAN evaluation metrics"
output: html_notebook
---

**Objective**
Observe the quality of the fake data as we iterate through the training epochs.
Generate mean and standard deviation of the fake data distribution over each epoch.

**Recipe**
1. Modify the original GAN script to support the input of the epochs and return a dataframe of essential values at each epoch iteration.


```{r}
# Get synthetic data and GAN evaluation metrics
# Generate fake data. Set the epochs.

library(rTorch)
library(tictoc)

tic()
# gan_noplot.py lives under notebooks/ folder
# gan <- reticulate::import("gan_noplot")   # import Python script
gan   <- import("gan_noplot_params_metrics")   # import available in rTorch
train <- gan$train
synth_data <- vector("list")
metrics    <- vector("list")
for (i in seq(1:10)) {
    message("Sample:", i)
    results = train(5000L)
    synth_data_ <- results[[1]]
    metrics_    <- results[[2]]
    # cat(sprintf("mean: %f; sd: %f\n", mean(ret_values), sd(ret_values)))
    # print(fivenum(ret_values))
    synth_data[[i]] <- data.frame(run = i, data = synth_data_)
    metrics[[i]]    <- cbind(i, metrics_)     # save samples in a list vector
}
toc()
```

```{r}
metrics
```


```{r}
# one set of fake_data
fake_data_sample <- results[[1]]
length(fake_data_sample)
```


```{r}
# one set of metrics
metrics_sample <- results[[2]]
dim(metrics_sample)
```


```
123   5000  10  1580.6s
123   5000  10  1394.0s
```

```{r}
save(metrics, synth_data, file = "metrics_s123e5000-2.rda")
```


## Dataframe of metrics for all epochs

```{r}
# extract key values from the list and return as dataframe
get_epoch <- function(x) {
    data.frame(run = x$i, epoch = x$epoch, synth_mean = x$mean_fake, synth_sd = x$sd_fake)
}

# mean and standard deviation table
mean_sd_10  <- lapply(metrics, get_epoch)
all_mean_sd <- do.call(rbind, mean_sd_10)
all_mean_sd
```

```{r}
# synthetic data
get_row <- function(x) {
    data.frame(run = x$i, data = x$synth_data_)    
}

lapply(synth_data, get_row)
```

```{r}
# dataframe for all the sythetic datasets
synth_data_df <- do.call(rbind, synth_data)
synth_data_df
```


```{r}
# histogram with ggplot2 for one run
library(dplyr)
library(ggplot2)

run <- all_mean_sd %>% 
    filter(run == 1) 

ggplot(run, aes(x = epoch, y = synth_mean)) +
    geom_point(alpha = 0.25)

ggplot(run, aes(x = epoch, y = synth_sd)) +
geom_point(alpha = 0.5)
```

```{r fig.height=4.5, fig.width=9}
# histogram with ggplot2
library(dplyr)
library(ggplot2)


ggplot(all_mean_sd, aes(x = epoch, y = synth_mean)) +
    geom_point(alpha = 0.3, size = 0.01, color = "darkgreen") +
    geom_hline(aes(yintercept = 4), linetype = "dotted") + 
    scale_y_continuous(name="Mean", breaks = c(0, 2, 4, 6, 8, 10, 12)) +
    scale_x_continuous(name="epoch", limits = c(0, 6000)) +
    facet_wrap(. ~ run, nrow = 2) +
    labs(title = "Mean")
```

```{r fig.height=4.5, fig.width=9}
# histogram with ggplot2
library(dplyr)
library(ggplot2)


ggplot(all_mean_sd, aes(x = epoch, y = synth_sd)) +
    geom_point(alpha = 0.3, size = 0.01, color = "blue") +
    geom_hline(aes(yintercept = 1), linetype = "dotted") + 
    scale_y_continuous(name="SD", breaks = c(0, 1, 2, 3, 4, 5)) +
    scale_x_continuous(name="epoch", limits = c(0, 6000)) +
    facet_wrap(. ~ run, nrow = 2) +
    labs(title = "Standard Deviation")
```

## Synthetic Data

```{r}
ggplot(synth_data_df, aes(x = data)) +
    geom_histogram(bins = 50) +
    facet_wrap(. ~ run, nrow=2)
```

```{r}
library(dplyr)

data_1 <- synth_data_df %>% 
    filter(run == 1) %>% 
    .$data

fivenum(data_1)    
mean(data_1)
sd(data_1)
```

```{r}
# run the mean and standard deviation on the synthetic data samples
library(dplyr)

synth_data_df %>% 
    group_by(run) %>% 
    summarise(mean(data), sd(data))

```

