---
title: "Retrieve and plot GAN quality over epochs"
output: html_notebook
---

## TOC
- 5.9000: Retrieve synthetic data and GAN evaluation metrics

**Objective**
Observe the quality of the fake data as we iterate through the training epochs.
Generate mean and standard deviation of the fake data distribution over each epoch.

**Recipe**
1. Modify the original GAN script to support the input of the epochs and return a dataframe of essential values at each epoch iteration.


```{r}
# Generate fake data. Set the epochs.

library(rTorch)
library(tictoc)

tic()
# gan_noplot.py lives under notebooks/ folder
# gan <- reticulate::import("gan_noplot")   # import Python script
gan   <- import("gan_noplot_params_df")   # import available in rTorch
train <- gan$train
sample <- vector("list")
for (i in seq(1:10)) {
    message("sample:", i)
    ret_values = train(500L)
    # cat(sprintf("mean: %f; sd: %f\n", mean(ret_values), sd(ret_values)))
    # print(fivenum(ret_values))
    sample[[i]] <- cbind(i, ret_values)     # save samples in a list vector
}
toc()
```

```
123   5000  10  1580.6s
123   5000  10  1394.0s
```

```{r}
metrics <- sample
save(metrics, file = "metrics_s123e500.rda")
```


```{r}
sample
```



```{r}
# extract key values from the list and return as dataframe
get_epoch <- function(x) {
    data.frame(run = x$i, epoch = x$epoch, mean = x$mean_fake, sd = x$sd_fake)
}

# mean and standard deviation table
mean_sd_10  <- lapply(sample, get_epoch)
all_mean_sd <- do.call(rbind, mean_sd_10)
all_mean_sd
```


```{r}
# histogram with ggplot2
library(dplyr)
library(ggplot2)

run <- all_mean_sd %>% 
    filter(run == 1) 

ggplot(run, aes(x = epoch, y = mean)) +
    geom_point(alpha = 0.25)

ggplot(run, aes(x = epoch, y = sd)) +
geom_point(alpha = 0.5)
```

```{r fig.height=4.5, fig.width=9}
# histogram with ggplot2
library(dplyr)
library(ggplot2)


ggplot(all_mean_sd, aes(x = epoch, y = mean)) +
    geom_point(alpha = 0.3, size = 0.01, color = "darkgreen") +
    geom_hline(aes(yintercept = 4), linetype = "dotted") + 
    scale_y_continuous(name="Mean", breaks = c(0, 2, 4, 6, 8, 10, 12)) +
    scale_x_continuous(name="epoch", limits = c(0, 6000)) +
    facet_wrap(. ~ run, nrow = 2) +
    labs(title = "Mean")
```

```{r fig.height=4.5, fig.width=9}
# histogram with ggplot2
library(dplyr)
library(ggplot2)


ggplot(all_mean_sd, aes(x = epoch, y = sd)) +
    geom_point(alpha = 0.3, size = 0.01, color = "blue") +
    geom_hline(aes(yintercept = 1), linetype = "dotted") + 
    scale_y_continuous(name="SD", breaks = c(0, 1, 2, 3, 4, 5)) +
    scale_x_continuous(name="epoch", limits = c(0, 6000)) +
    facet_wrap(. ~ run, nrow = 2) +
    labs(title = "Standard Deviation")
```
